disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-11-21 article.Rnw
Tweak.
Were getting stick for this in the point-polygon paper so best to hammer the exact point home wherever we can.

Methods for estimating high-resolution risk maps from aggregated response data over large spatial regions are 
becoming increasingly sought after in disease risk mapping~\cite{li2012log, diggle2013spatial, wilson2017pointless}, especially in malaria mapping~\cite{sturrock2014fine, sturrock2016mapping}. 
Disaggregation regression, first applied in species distribution modelling in ecology~\cite{keil2013downscaling, barwell2014can} has now become an important method in disease risk mapping \cite{falciparum2019, vivax2019}. 
The aggregation of response data over large heterogenous regions is problematic for understanding the fine-scale distribution. However, by using fine-scale information from related covariates we can inform the hetrogeneity of the response variable of interest within the agreggated area.

Disaggregation modelling is unorthodox as the predictions are at a different scale to the response data, i.e. the number of rows in the covariate data is different to that of the repsonse data. Traditional spatial modelling software package, \pkg{INLA}~\cite{rue2009approximate}, has been shown to very useful in a wide variety of circumstances, however it is not flexible enough for the unorthodox nature of the disaggregation problem. Disaggregation models can be implemented in \pkg{TMB}~\cite{tmb2016} with a lot of flexibility, however the data manipulation required to format the model objects and construct the model definition in C++ is non-trivial. The \pkg{disaggregation} package allows this process to be streamlined, to make it easy for the user to run disaggregation models with some degree of flexibility.

>>>>

Methods for estimating high-resolution risk maps from aggregated response data over large spatial regions are 
becoming increasingly sought after in disease risk mapping~\cite{li2012log, diggle2013spatial, wilson2017pointless}, especially in malaria mapping~\cite{sturrock2014fine, sturrock2016mapping}. 
Disaggregation regression, first applied in species distribution modelling in ecology~\cite{keil2013downscaling, barwell2014can} has now become an important method in disease risk mapping \cite{falciparum2019, vivax2019}. 
The aggregation of response data over large heterogenous regions is problematic for making fine-scale predictions. However, by using fine-scale information from related covariates we can inform the hetrogeneity of the response variable of interest within the agreggated area.

Disaggregation modelling is unorthodox as the predictions are at a different scale to the response data, i.e. the number of rows in the covariate data is different to that of the response data. The spatial modelling software package, \pkg{INLA}~\cite{rue2009approximate}, has been shown to very useful in a wide variety of circumstances, however it is not flexible enough for the unorthodox nature of the disaggregation problem except in the special case of the linear link function \cite{wilson2017pointless}. Disaggregation models can be implemented in \pkg{TMB}~\cite{tmb2016} with a lot of flexibility, however the data manipulation required to format the model objects and construct the model definition in C++ is non-trivial. The \pkg{disaggregation} package allows this process to be streamlined, to make it easy for the user to run disaggregation models with some degree of flexibility.
